---
title: "LandWeb_output Manual"
subtitle: "v.`r SpaDES.core::moduleMetadata(module = 'LandWeb_output', path = '..')$version`"
date: "Last updated: `r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    theme: sandstone
    number_sections: false
    df_print: paged
    keep_md: yes
editor_options:
  chunk_output_type: console
  bibliography: citations/references_LandWeb_output.bib
link-citations: true
always_allow_html: true
---

# LandWeb_output Module

<!-- the following are text references used in captions for LaTeX compatibility -->
(ref:LandWeb-output) *LandWeb_output*

```{r setup-LandWeb-output, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold") ## change to eval = TRUE if all chunks are to be evaluated

if (!require(dplyr)) {
  install.packages("dplyr")
  library(dplyr)
}
```

#### Authors:

`r paste(as.character(SpaDES.core::moduleMetadata(module = "LandWeb_output", path = '..')$authors), sep = ', ')`
<!-- ideally separate authors with new lines, '\n' not working -->

## Module Overview

### Module summary

This module saves LandR Biomass outputs for use with LandWeb post-processing.

### Module inputs and parameters

Table \@ref(tab:moduleInputs-LandWeb-output) shows the full list of module inputs.

```{r moduleInputs-LandWeb-output, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
df_inputs <- SpaDES.core::moduleInputs("LandWeb_output", "..")
knitr::kable(df_inputs,
             caption = "List of (ref:LandWeb-output) input objects and their description.") %>%
  kableExtra::kable_styling(latex_options = "scale_down", full_width = FALSE)
```

Provide a summary of user-visible parameters (Table \@ref(tab:moduleParams-LandWeb-output))


```{r moduleParams-LandWeb-output, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
df_params <- SpaDES.core::moduleParams("LandWeb_output", "..")
knitr::kable(df_params, caption = "List of (ref:LandWeb-output) parameters and their description.") %>%
  kableExtra::kable_styling(latex_options = "scale_down", full_width = FALSE)
```

### Module outputs

Description of the module outputs (Table \@ref(tab:moduleOutputs-LandWeb-output)).

```{r moduleOutputs-LandWeb-output, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
df_outputs <- SpaDES.core::moduleOutputs("LandWeb_output", "..")
knitr::kable(df_outputs, caption = "List of (ref:LandWeb-output) outputs and their description.") %>%
  kableExtra::kable_styling(latex_options = "scale_down", full_width = FALSE)
```

### Links to other modules

Originally developed as part of the [LandWeb](https://github.com/PredictiveEcology/LandWeb) project.

### Getting help

<https://github.com/fRI-Research/LandWeb_output/issues>
